---
title: "Explore pca in stock data"
documentclass: ctexart
output:
  html_notebook: 
    fig_caption: yes
    number_sections: yes
    toc: yes
    toc_depth: 4
    toc_float:
      collapsed: no
      smooth_scroll: no
      padding-left: yes
    df_print: paged
    theme: cerulean
    highlight: pygments
    code_folding: hide
  html_document:
    fig_caption: yes
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: false
      smooth_scroll: false
    df_print: paged
    theme: cerulean
    highlight: pygments
    code_folding: hide
params:
  indcd_group:
    label: 'Indcd Group:'
    input: text
    value: 'C37, C38, C39'
  cs_date:
    label: 'Year:'
    input: text
    value: '2018-12-31'
---


```{css, echo=FALSE}

/*Setting for scrollable code/text*/ 

pre {
  max-height: 400px;
  overflow-y: auto;
}

pre[class] {
  max-height: 400px;
}

/*Setting for TOC and outlook*/

div.main-container {
  max-width: 100% !important;
}

.tocify {
  max-width: 20% !important;
}

.toc-content {
  padding-left: 5px !important;
}
```

```{r setup, include=FALSE}


# General packages
library(tidyverse)
library(gridExtra)
library(DT)
library(plotly)
library(glue)

# Special packages
library(FactoMineR)
library(factoextra)
library(FactoInvestigate)

# My packages
devtools::load_all()

# Set global options for knitr
knitr::opts_chunk$set(
  fig.align = "center",
  fig.show = "hold",
  message = FALSE,
  warning = FALSE,
  collapse = TRUE,
  results = "hold",
  comment = "#>",
  out.width = "80%",
  tidy = "styler"
)
```
# Prepare data

Parameters for loading data:

**Industry Group:** *`r knitr::combine_words(params$indcd_group)`*

**Date of Cross-sectional data:** *`r params$cs_date`*

```{r, class.source = 'fold-show'}
indcd_group <- stringr::str_split(params$indcd_group, pattern = ",")
indcd_group <- stringr::str_trim(unlist(indcd_group))
cs_date <- stringr::str_trim(params$cs_date)

csbl_vars <- load_csbl_vars()

df_pca_raw <-
  csbl_vars %>%
  dplyr::filter(indcd %in% indcd_group) %>%
  tidyr::separate(id, into = c("date", "period", "stkcd"), sep = "_") %>%
  dplyr::filter(grepl(cs_date, date)) %>%
  dplyr::select(-c("date", "period")) %>%
  # Use median for numeric field of multiple period series of stock
  # Use mode numbers for non-numeric filed of multiple period series of stock
  dplyr::group_by(stkcd) %>%
  dplyr::summarise(
    indcd = names(which.max(table(indcd))),
    across(where(is.numeric), median),
    .groups = "drop"
  ) %>%
  # Scale data
  dplyr::mutate(across(where(is.numeric), scale)) %>%
  tibble::column_to_rownames(var = "stkcd")


```



# Handle Missing Value

```{r}
df_pca <-
  df_pca_raw %>%
  na.omit()
```

## Pattern of missing value
```{r}

VIM::aggr(df_pca_raw, numbers = TRUE, prop = TRUE)

```

## Impute missing value


### Estimate ncp for imputation

```{r, }

estimate_ncp_PCA <- missMDA::estim_ncpPCA(df_pca_raw,
  method.cv = "gcv",
  quali.sup = 1
)
plot(estimate_ncp_PCA$criterion ~ names(estimate_ncp_PCA$criterion),
  xlab = "number of dimensions"
)
```

Estimated ncp for impute missing is **`r estimate_ncp_PCA$ncp `**


### Imputed missing values

```{r}

impute_res <- missMDA::imputePCA(df_pca_raw,
  ncp = estimate_ncp_PCA$ncp,
  quali.sup = 1
)

df_pca <- impute_res$completeObs
```




# Compute PCA

```{r results = "markup", class.source = 'fold-show'}
# Compute Q-mode PCA with prcomp() by using SVD
prcomp_res <- prcomp(df_pca[, -1], scale. = TRUE)
summary(prcomp_res)

# Compute R-mode PCA with princomp by using eigen value on correlation or covariance matrix
princomp_res <- princomp(df_pca[, -1], cor = TRUE)
summary(princomp_res)

# Compute PCA with PCA
pca_res <- FactoMineR::PCA(df_pca, quali.sup = 1, graph = FALSE)
summary(pca_res)
```

# Study of the outliers

## Result of outlies detection

```{r, results = "asis"}

outliers_res_string <- capture.output({
  invisible(
    outliers_res <- FactoInvestigate::outliers(pca_res)
  )
})

outliers_res_string <- paste(outliers_res_string, collapse = "\n")

# Remove code in results
outliers_res_string <- stringr::str_remove_all(
  outliers_res_string,
  pattern = "```[\\w\\W]*```"
)

# Remove Figure caption in results
outliers_res_string <- stringr::str_remove_all(
  outliers_res_string,
  pattern = "\\*\\*Figure[\\w\\W]*\\\\*\\*"
)

cat(outliers_res_string, "\n")

```


# Inertia distribution

The eigenvalues measure the amount of variation retained by each principal component. Eigenvalues are large for the first PCs and small for the subsequent PCs. That is, the first PCs corresponds to the directions with the maximum amount of variation in the data set.

Eigenvalues can be used to determine the number of principal components to
retain after PCA:

* An eigenvalue > 1 indicates that PCs account for more variance than
accounted by one of the original variables in standardized data. This
is commonly used as a cutoff point for which PCs are retained. This
holds true only when the data are standardized.

* You can also limit the number of component to that number that
accounts for a certain fraction of the total variance. For example, if
you are satisfied with 70% of the total variance explained then use the
number of components to achieve that.

## Decomposition of total inertia {.tabset }



### Plots {.unnumbered}
```{r fig.align = "default", fig.show= 'hold', out.width= "30%" }
factoextra::fviz_eig(prcomp_res, addlabels = TRUE) +
  labs(subtitle = "compute by prcomp()")

factoextra::fviz_eig(princomp_res, addlabels = TRUE) +
  labs(subtitle = "compute by princomp()")

factoextra::fviz_eig(pca_res, addlabels = TRUE) +
  labs(subtitle = "compute by PCA()")
```



### Values {.unnumbered}

```{r}
eig_res <- factoextra::get_eig(pca_res)
eig_res

```


## Analysis of inertia distribution


Analysis of the inertia distribution among each axis, the amount and the significativity.

```{r , cache = TRUE, results = "asis"}

inerital_res_string <- capture.output({
  invisible(
    best_ncp <- FactoInvestigate::inertiaDistrib(pca_res, q = 0.95, time = "10s")
  )
})

inerital_res_string <- paste(inerital_res_string, collapse = "\n")

# Remove code in results
inerital_res_string <- stringr::str_remove_all(
  inerital_res_string,
  pattern = "```[\\w\\W]*```"
)

# Remove Figure caption in results
inerital_res_string <- stringr::str_remove_all(
  inerital_res_string,
  pattern = "\\*\\*Figure[\\w\\W]*\\\\*\\*"
)

cat(inerital_res_string, "\n")
```


# Graph of variables

```{r}
var <- factoextra::get_pca_var(pca_res)
var
```


## Correlation circle

The correlation between a variable and a principal component (PC) is used as
the coordinates of the variable on the PC. The representation of variables
differs from the plot of the observations: The observations are represented by
their projections, but the variables are represented by their correlations

The plot is also known as variable correlation plots. It shows the
relationships between all variables. It can be interpreted as follow:

* Positively correlated variables are grouped together.

* Negatively correlated variables are positioned on opposite sides of the
plot origin (opposed quadrants).

* The distance between variables and the origin measures the quality of
the variables on the factor map. Variables that are away from the origin
are well represented on the factor map.

```{r}
factoextra::fviz_pca_var(pca_res, col.var = "black", repel = TRUE)
```

## Quality of representation

The quality of representation of the variables on factor map is called cos2
(square cosine, squared coordinates).

* The cos2 values are used to estimate the quality of the representation

  * A high cos2 indicates a good representation of the variable on the
principal component. In this case the variable is positioned close to
the circumference of the correlation circle.

  * A low cos2 indicates that the variable is not perfectly represented by
the PCs. In this case the variable is close to the center of the circle.

* The closer a variable is to the circle of correlations, the better its
representation on the factor map (and the more important it is to
interpret these components)

* Variables that are closed to the center of the plot are less important
for the first components.

```{r}

# Find vars of top n cos2
top_cos2_var <- var$cos2 %>%
  tibble::as_tibble(rownames = "id") %>%
  dplyr::slice_max(order_by = Dim.1 + Dim.2 + Dim.3 + Dim.4, n = 10) %>%
  dplyr::arrange(desc(across(starts_with("Dim")))) %>%
  tibble::column_to_rownames(var = "id") %>%
  as.matrix()

corrplot::corrplot(top_cos2_var, is.corr = FALSE)


# Cos2 of variables to PC1 and PC2
factoextra::fviz_cos2(pca_res, choice = "var", axes = 1:2, top = 10)

# Cos2 of variables to PC3 and PC4
factoextra::fviz_cos2(pca_res, choice = "var", axes = 3:4, top = 10)

# Visualize cos2 of variables on plane of PC1 and PC2
factoextra::fviz_pca_var(
  pca_res,
  axes = 1:2,
  col.var = "blue",
  alpha.var = "cos2",
  repel = TRUE,
  title = "Variables on Dim-1-2 of PCA"
)

# Visualize cos2 of variables on plane of PC1 and PC2
fviz_pca_var(
  pca_res,
  axes = 3:4,
  col.var = "blue",
  alpha.var = "cos2",
  linesize = "cos2",
  repel = TRUE,
  title = "Variables on Dim-3-4 of PCA"
)
```


## Contributions to PCs

The contributions of variables in accounting for the variability in a given
principal component are expressed in percentage.

* Variables that are correlated with PC1 (i.e., Dim.1) and PC2 (i.e.,
Dim.2) are the most important in explaining the variability in the data
set.

* Variables that do not correlated with any PC or correlated with the last
dimensions are variables with low contribution and might be removed to simplify
the overall analysis.

```{r}
# Find vars of top n contributions
top_contrib_var <- var$contrib %>%
  tibble::as_tibble(rownames = "id") %>%
  dplyr::slice_max(order_by = Dim.1 + Dim.2 + Dim.3 + Dim.4, n = 10) %>%
  dplyr::arrange(desc(across(starts_with("Dim")))) %>%
  tibble::column_to_rownames(var = "id") %>%
  as.matrix()

corrplot::corrplot(top_contrib_var,
  is.corr = FALSE,
  title = "Top 10 variables of contribuions"
)


# Contributions of variables to PC1 and PC2
fviz_contrib(pca_res, choice = "var", axes = 1:2, top = 10)

# Contributions of variables to PC3 and PC4
fviz_contrib(pca_res, choice = "var", axes = 3:4, top = 10)

fviz_pca_var(pca_res,
  col.var = "contrib",
  axes = 1:2,
  # gradient.cols = ggsci::pal_gsea()(12),
  gradient.cols = colorRampPalette(c("blue", "red"), alpha = TRUE)(12),
  title = "Variables on Dim-1-2 of PCA"
)

fviz_pca_var(pca_res,
  col.var = "contrib",
  axes = 3:4,
  # gradient.cols = ggsci::pal_gsea()(12),
  gradient.cols = colorRampPalette(c("blue", "red"), alpha = TRUE)(12),
  title = "Variables on Dim-3-4 of PCA"
)
```



# Graph of individuals

```{r}
ind <- factoextra::get_pca_ind(pca_res)
ind
```

## Quality of representation

```{r}

# Find individuals of top n cos2
top_cos2_ind <- ind$cos2 %>%
  tibble::as_tibble(rownames = "id") %>%
  dplyr::slice_max(order_by = Dim.1 + Dim.2 + Dim.3 + Dim.4, n = 10) %>%
  dplyr::arrange(desc(across(starts_with("Dim")))) %>%
  tibble::column_to_rownames(var = "id") %>%
  as.matrix()

corrplot::corrplot(top_cos2_ind, is.corr = FALSE)

# Cos2 of variables to PC1 and PC2
factoextra::fviz_cos2(pca_res, choice = "ind", axes = 1:2) +
  theme(axis.text.x = element_text(angle = -90))

# Cos2 of variables to PC3 and PC4
factoextra::fviz_cos2(pca_res, choice = "ind", axes = 3:4) +
  theme(axis.text.x = element_text(angle = -90))

# Visualize cos2 of variables on plane of PC1 and PC2
factoextra::fviz_pca_ind(
  pca_res,
  axes = 1:2,
  geom = "point",
  col.ind = "red",
  alpha.ind = "cos2",
  title = "Individuals on Dim-1-2 of PCA"
)

# Visualize cos2 of variables on plane of PC3 and PC4
fviz_pca_ind(
  pca_res,
  axes = 3:4,
  geom = "point",
  col.ind = "red",
  alpha.ind = "cos2",
  title = "Individuals on Dim-3-4 of PCA"
)
```


## Contributions to PCs

```{r}

# Find individuals of top n contributions
top_contrib_ind <- ind$contrib %>%
  tibble::as_tibble(rownames = "id") %>%
  dplyr::slice_max(order_by = Dim.1 + Dim.2 + Dim.3 + Dim.4, n = 10) %>%
  dplyr::arrange(desc(across(starts_with("Dim")))) %>%
  tibble::column_to_rownames(var = "id") %>%
  as.matrix()
corrplot::corrplot(top_contrib_ind, is.corr = FALSE)

# Contributions of individuals to PC1 and PC2
factoextra::fviz_contrib(pca_res, choice = "ind", axes = 1:2) +
  theme(axis.text.x = element_text(angle = -90))

# Contributions of individuals to PC3 and PC4
factoextra::fviz_contrib(pca_res, choice = "ind", axes = 3:4) +
  theme(axis.text.x = element_text(angle = -90))

factoextra::fviz_pca_ind(pca_res,
  axes = 1:2,
  geom = "point",
  pointsize = "contrib",
  col.ind = "red",
  title = "Individuals on Dim-1-2 of PCA"
)

factoextra::fviz_pca_ind(pca_res,
  axes = 3:4,
  geom = "point",
  pointsize = "contrib",
  col.ind = "red",
  title = "Individuals on Dim-3-4 of PCA"
)
```


# Description of the plane 1:2

## Description by varables

Identify the most significantly associated variables with a given principal component.

```{r}

dim_desc <- FactoMineR::dimdesc(pca_res, axes = c(1, 2), proba = 0.5)

knitr::kable(dim_desc$Dim.1$quanti,
  caption = "Dim.1 description by the quantitative variable"
)

knitr::kable(dim_desc$Dim.2$quanti,
  caption = "Dim.1 description by the quantitative variable"
)
```



### Variables factor map {.tabset .tabset-fade .tabset-pills}


```{r}
# Find vars shown best on the plate
focus_vars <- FactoInvestigate::selection(
  pca_res,
  margin = 2, # computes on the active variables
  selec = "cos2"
)

if (length(focus_vars$drawn) == 0) {
  focus_vars <- FactoInvestigate::selection(
    pca_res,
    margin = 2, # computes on the active variables
    selec = "cos2 10"
  )
}
```


#### Plot by FactoMineR {.unnumbered}

```{r}
p <- FactoMineR::plot.PCA(pca_res,
  choix = "var",
  habillage = "contrib",
  select = focus_vars$drawn,
  cex = 0.9
)

p <- p + labs(
  title = "Varables factor map(PCA)",
  subtitle = focus_vars$what.drawn
)

p
```

#### Plot by factoextra  {.unnumbered}

```{r}
p <- factoextra::fviz_pca_var(pca_res,
  repel = TRUE,
  col.var = "contrib",
  alpha.var = "cos2",
  cex = 0.5,
  # gradient.cols = ggsci::pal_gsea()(12),
  gradient.cols = colorRampPalette(c("blue", "red"), alpha = TRUE)(12),
  label.select = focus_vars$drawn,
)

p <- p + labs(
  title = "Varables factor map(PCA)",
  subtitle = focus_vars$what.drawn
)

p
```

### Qualitative factor map {.tabset .tabset-fade .tabset-pills}

```{r}

if (!is.null(dim_desc$Dim.1$category)) {
  knitr::kable(dim_desc$Dim.1$category,
    caption = "Dim.1 description by the qualitative variable"
  )
}

if (!is.null(dim_desc$Dim.2$category)) {
  knitr::kable(dim_desc$Dim.2$category,
    caption = "Dim.2 description by the qualitative variable"
  )
}
```


```{r}

# Find factors shown best on the plate
focus_factors <- FactoInvestigate::selection(
  pca_res,
  margin = 3, # computes on the supplementary variables
  selec = "cos2"
)
```


#### Plot by FactoMineR {.unnumbered}

```{r}
p <- FactoMineR::plot.PCA(pca_res,
  axes = 1:2,
  choix = "ind",
  select = focus_factors$drawn,
  invisible = c("ind", "ind.sup")
)

p <- p + labs(
  title = "Qualitative factor map(PCA)",
  subtitle = focus_factors$what.drawn
)

p
```

#### Plot by factoextra {.unnumbered}

```{r}
p <- factoextra::fviz_pca_ind(
  pca_res,
  invisible = c("ind", "ind.sup")
)
p <- factoextra::fviz_add(p,
  pca_res$quali.sup$coord[focus_factors$drawn, ],
  color = "red"
)

xlims <- range(pca_res$quali.sup$coord[focus_factors$drawn, ][, "Dim.1"]) * 1.5
ylims <- range(pca_res$quali.sup$coord[focus_factors$drawn, ][, "Dim.2"]) * 1.5

p <- p + labs(
  title = "Qualitative factor map(PCA)",
  subtitle = focus_factors$what.drawn
) + xlim(xlims) + ylim(ylims)

p
```


## Description by individuals
### Individuals factor map {.tabset .tabset-fade .tabset-pills}

```{r}
# Find individuals with higher contributions to the plane
focus_inds <- FactoInvestigate::selection(
  pca_res,
  margin = 1, # computes on the individuals
  selec = "contrib"
)

if (length(focus_inds$drawn) == 0) {
  focus_inds <- FactoInvestigate::selection(
    pca_res,
    margin = 1, # computes on the individuals
    selec = "contrib 10"
  )
}
```

#### Plot by FactoMineR {.unnumbered}

```{r}
# Plot individuals by FactoMineR::plot.PCA

# FactoMineR::plot.PCA(pca_res,
#          invisible = c('ind.sup'),
#          select = 'contrib  5',
#          select = focus_inds$drawn,
#          habillage = 1,
#          label =c('ind','quali'))

p <- FactoMineR::plotellipses(pca_res,
  invisible = c("ind.sup"),
  # select = 'contrib  5',
  select = focus_inds$drawn,
  habillage = 1,
  label = c("ind", "quali")
)

p <- p + labs(
  title = "Individuals factor map (PCA)",
  subtitle = focus_inds$what.drawn
)

p
```

#### Plot by factoextra {.unnumbered}

```{r }
# Plot individuals by factoextra::fviz_pca_ind

# Use contrib for size, Cos2 for alpha
p <- factoextra::fviz_pca_ind(
  pca_res,
  repel = FALSE,
  col.ind = "black",
  fill.ind = df_pca$indcd,
  alpha.ind = "cos2",
  pointshape = 21,
  pointsize = "contrib",
  labelsize = 3,
  addEllipses = TRUE,
  ellipse.type = "confidence",
  label.select = focus_inds$drawn,
  legend.title = list(
    color = "Indcd",
    fill = "Indcd"
  ),
  palette = "aaas"
)
p <- factoextra::fviz_add(p,
  pca_res$quali.sup$coord,
  color =  ggsci::pal_aaas()(nrow(pca_res$quali.sup$coord))
)

p <- p + labs(
  title = "Individuals factor map(PCA)",
  subtitle = focus_inds$what.drawn
)

p
```


## Description by variables and individuals jontly

### Joint factors map

```{r}

p <- factoextra::fviz_pca_biplot(
  pca_res,
  axes = c(1,2),

  # Setting for individuals
  habillage = "none",
  col.ind = "black",
  fill.ind = df_pca$indcd,
  alpha.ind = "cos2",
  pointshape = 21,
  pointsize = "contrib",
  addEllipses = TRUE,
  ellipse.type = "confidence",
  # select.ind = list(name = focus_inds$drawn),
  palette = "aaas",

  # Setting for vars
  col.var = "contrib",
  alpha.var = "cos2",
  # gradient.cols = ggsci::pal_gsea()(12),
  gradient.cols = colorRampPalette(c("blue", "red"), alpha = TRUE)(12),
  # select.var = list(name = focus_vars$drawn),

  
  # Common setting
  repel = TRUE,
  labelsize = 3,
  label.select = c(focus_inds$drawn, focus_vars$drawn),
  legend.title = list(
    fill = "indcd",
    color = "Contrib"
  )
)

p <- factoextra::fviz_add(p,
  pca_res$quali.sup$coord,
  color = ggsci::pal_aaas()(nrow(pca_res$quali.sup$coord))
)

p <- p + labs(
  title = "Biplot map(PCA)",
  subtitle = glue::glue("{focus_vars$what.drawn}\n{focus_inds$what.drawn}")
)

p
```

### Joint factors description


```{r, results = "asis"}

# dim_desc_res <-
#
#   FactoInvestigate::description(pca_res, dim = c(1, 2))
#
# cat(dim_desc_res, "\n")

dim_desc_res_string <- capture.output({
  invisible(
    FactoInvestigate::description(pca_res, dim = c(1, 2))
  )
})

dim_desc_res_string <- paste(dim_desc_res_string, collapse = "\n")

# Remove code in results
dim_desc_res_string <- stringr::str_remove_all(
  dim_desc_res_string,
  pattern = "```[\\w\\W]*```"
)

# Remove Figure caption in results
dim_desc_res_string <- stringr::str_remove_all(
  dim_desc_res_string,
  pattern = "\\*\\*Figure[\\w\\W]*\\\\*\\*"
)

cat(dim_desc_res_string, "\n")
```


# Classification


## Find clusters by HCPC

The HCPC (Hierarchical Clustering on Principal Components) approach
allows us to combine the three standard methods used in multivariate data
analyses:

1. Principal component methods (PCA, CA, MCA, FAMD, MFA),
2. Hierarchical clustering and
3. Partitioning clustering, particularly the k-means method.

The algorithm of the HCPC method, as implemented in the FactoMineR
package, can be summarized as follow:

1. Compute principal component methods: PCA, (M)CA or MFA
depending on the types of variables in the data set and the structure of
the data set. At this step, you can choose the number of dimensions to be
retained in the output by specifying the argument ncp. The default value
is 5.

2. Compute hierarchical clustering: Hierarchical clustering is performed
using the Ward's criterion on the selected principal components. Ward
criterion is used in the hierarchical clustering because it is based on the
multidimensional variance like principal component analysis.

3. Choose the number of clusters based on the hierarchical tree: An initial
partitioning is performed by cutting the hierarchical tree.

4. Perform K-means clustering to improve the initial partition obtained
from hierarchical clustering. The final partitioning solution, obtained
after consolidation with k-means, can be (slightly) different from the one
obtained with the hierarchical clustering.


```{r, echo = FALSE}
hcpc_res <- FactoMineR::HCPC(pca_res, nb.clust = -1, graph = FALSE)

cluster_result_hcpc <- hcpc_res$data.clust %>%
  tibble::rownames_to_column(var = "stkcd") %>%
  dplyr::mutate(
    indcd = as.character(indcd),
    indname = zstexplorer:::code2name(indcd),
    stkname = zstexplorer:::code2name(stkcd),
    cluster = as.factor(clust)
  ) %>%
  dplyr::select(stkcd, stkname, indcd, indname, cluster)

DT::datatable(cluster_result_hcpc,
  caption = "Clustering Results of HCPC",
  filter = "top",
  extensions = "Scroller",
   rownames = FALSE,
  options = list(
    columnDefs = list(
      list(className = "dt-left", targets = "_all")
    ),
    pageLength = 5,
    dom = "ltir",
    deferRender = TRUE,
    scrollY = 180,
    scrollX = TRUE,
    scroller = TRUE
  )
)
```
Found ```r hcpc_res$call$t$nb.clust ``` clusters.
 
 
## Cluster Description {.tabset .tabset-fade .tabset-pills}

### Some individuals in clusters {.unnumbered}
```{r}

colnames <- names(hcpc_res$data.clust)
colnames <- c("id", colnames)

data_clust <- hcpc_res$data.clust %>%
  tibble::as_tibble(rownames = "id")


data_clust_sample <- data_clust %>%
  dplyr::group_by(clust) %>%
  dplyr::slice_sample(n = 3)

data_clust_focus <- data_clust %>%
  dplyr::filter(id %in% focus_inds$drawn) %>%
  dplyr::arrange(clust)

knitr::kable(data_clust_sample, caption = "Some individuals in clusters")
```

### Desc by the variables {.unnumbered}   

```{r, class.source = 'fold-show'}
hcpc_res$desc.var
```
### Desc by the dimensions{.unnumbered}
```{r, class.source = 'fold-show'}
hcpc_res$desc.axes
```

### Desc by the individuals {.unnumbered}
```{r, class.source = 'fold-show'}
hcpc_res$desc.ind

```







## Classifcation map {.tabset .tabset-fade .tabset-pills}

```{r}

# Representative individuals of each cluster
rep_inds <- purrr::map(hcpc_res$desc.ind$para, ~ names(.x))
rep_inds <- purrr::reduce(rep_inds, .f = c)


data_clust_rep_inds <- data_clust %>%
  dplyr::filter(id %in% rep_inds) %>%
  dplyr::arrange(clust)

knitr::kable(data_clust_rep_inds, caption = "Representive individuals of clusters")

```


### Plot by FactoMineR {.unnumbered}

```{r}

FactoMineR::plot.HCPC(
  hcpc_res,
  axes = c(1, 2),
  choice = "tree",
  title = "Tree - Hierarchical Clustering"
)

FactoMineR::plot.HCPC(
  hcpc_res,
  axes = c(1, 2),
  choice = "bar",
  title = "Bar - Hierarchical Clustering"
)

FactoMineR::plot.HCPC(
  hcpc_res,
  axes = c(1, 2),
  choice = "map",
  draw.tree = TRUE,
  select = rep_inds,
  title = "Map - clustering on the factor map"
)

FactoMineR::plot.HCPC(
  hcpc_res,
  axes = c(1, 2),
  choice = "3D.map",
  centers.plot = TRUE,
  title = "3D.map - Hierarchical clustering on the factor map"
)
```

### Plot by factoextra {.unnumbered}

```{r}

# Dendrogram by hierarchical clustering
factoextra::fviz_dend(hcpc_res,
  cex = 0.7, # Label size
  palette = "aaas", # Color palette see ?ggpubr::ggpar
  rect = TRUE, rect_fill = TRUE, # Add rectangle around groups
  rect_border = "aaas", # Rectangle color
  labels_track_height = 0.8, # Augment the room for labels
  title = "Dengrogram of individuals clusters by HCPC"
)

# Cluster by hierarchical clustering
factoextra::fviz_cluster(hcpc_res,
  repel = TRUE, # Avoid label overlapping
  geom = c("point", "text"),
  label.select = rep_inds,
  labelsize = 10,
  palette = "aaas", # Color palette see ?ggpubr::ggpar
  ggtheme = theme_minimal(),
  main = "Map of individuals clusters by HCPC"
)
```

## Classifcation description

```{r, results = "asis"}

class_res_string <- capture.output({
  invisible(
    class_res <- FactoInvestigate::classif(pca_res, graph = FALSE)
  )
})

class_res_string <- paste(class_res_string, collapse = "\n")

# Remove code in results
class_res_string <- stringr::str_remove_all(
  class_res_string,
  pattern = "```[\\w\\W]*```"
)

# Remove Figure caption in results
class_res_string <- stringr::str_remove_all(
  class_res_string,
  pattern = "\\*\\*Figure[\\w\\W]*\\.\\*\\*"
)

cat(class_res_string, "\n")
```

## Cluster mapping to industry and stocks

```{r}

cluster_mapping_hcpc <- cluster_result_hcpc %>%
  dplyr::nest_by(cluster) %>%
  dplyr::mutate(
    indcds = list(sort(unique(data$indcd))),
    indnames = list(sort(unique(data$indname))),
    stkcds = list(sort(unique(data$stkcd))),
    stknames = list(sort(unique(data$stkname)))
  ) %>%
  dplyr::select(-c("data", "indcds", "stkcds"))

DT::datatable(cluster_mapping_hcpc,
  caption = "Mapping between clusters and industry/stocks",
  filter = "top",
  extensions = "Scroller",
  rownames = FALSE,
  options = list(
    columnDefs = list(
      list(className = "dt-left", targets = "_all")
    ),
    pageLength = 10,
    dom = "ltir",
    deferRender = TRUE,
    scrollY = 180,
    scrollX = TRUE,
    scroller = TRUE
  )
)
```



## Appendix {-}

### A.1 Indcd reference {-}

```{r, cache = TRUE}
stock_db <- zstexplorer::stock_db()
industry_info <- zstmodelr::get_industry_info(stock_db)

DT::datatable(industry_info,
  caption = "Information about indcd",
  filter = "top",
  extensions = "Scroller",
  options = list(
    columnDefs = list(
      list(className = "dt-left", targets = "_all")
    ),
    pageLength = 5,
    dom = "ltir",
    deferRender = TRUE,
    scrollY = 180,
    scrollX = TRUE,
    scroller = TRUE
  )
)
```

### A.2 Stkcd reference {-}

```{r, cache = TRUE}
stock_db <- zstexplorer::stock_db()
stock_info <- zstmodelr::get_stock_info(stock_db)

DT::datatable(stock_info,
  caption = "Information about stkcd",
  filter = "top",
  extensions = "Scroller",
  options = list(
    columnDefs = list(
      list(className = "dt-left", targets = "_all")
    ),
    pageLength = 5,
    dom = "ltir",
    deferRender = TRUE,
    scrollY = 180,
    scrollX = TRUE,
    scroller = TRUE
  )
)
```

### A.3 Factor reference {-}

```{r, cache = TRUE}
stock_db <- zstexplorer::stock_db()
factors_info <- zstmodelr::get_factors_info(stock_db)

DT::datatable(factors_info,
  caption = "Information about factors",
  filter = "top",
  extensions = "Scroller",
  options = list(
    columnDefs = list(
      list(className = "dt-left", targets = "_all")
    ),
    pageLength = 5,
    dom = "ltir",
    deferRender = TRUE,
    scrollY = 180,
    scrollX = TRUE,
    scroller = TRUE
  )
)
```

### A.4 Indicator reference {-}

```{r, cache = TRUE}
stock_db <- zstexplorer::stock_db()
indicators_info <- zstmodelr::get_indicators_info(stock_db)

DT::datatable(indicators_info,
  caption = "Information about indicators",
  filter = "top",
  extensions = "Scroller",
  options = list(
    columnDefs = list(
      list(className = "dt-left", targets = "_all")
    ),
    pageLength = 5,
    dom = "ltir",
    deferRender = TRUE,
    scrollY = 180,
    scrollX = TRUE,
    scroller = TRUE
  )
)
```
